%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Jordan Spangenberg}
\address{Portland, OR}
\contacts{(541) 720-2859 \linebreak jordan.spang@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Junior QA Engineer}{Ubiquiti Networks}{October 2019 - December 2019}
			Unifi Network Controller
			\begin{itemize}
				\item Developed end-to-end automated testing simulating user activity using JavaScript, NodeJS, and the Codecept
framework.
				\item Designed and developed automated testing tools. BASH shell, Python, and NodeJs scripts to manage devices.
				\item Diagnosed and debugged database (MongoDB) and REST API errors.
				\item Developed asynchronous NodeJS command line and testing tools.
				\item Experienced with Jenkins, Travis CI, and Docker building CI pipelines and automating build testing.
				\item Experienced with issue tracking software and integrating with automated build and testing tools.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Full-Stack Web Developer, Intern}{Prosper IT Consulting}{March 2019 - May 2019}	
			Assisted team members with software engineering projects, working cross-functionally to gather requirements and align tasks within an Agile environment. Projects include:
			\begin{itemize}
				\item \textbf{ASP.NET MVC Construction Client Website}: Developed user roles and permissions to restrict views and prevent unauthorized actions. Created a dashboard to view jobs, schedules, news, and users. Refactored, debugged, and cleaned register, login, and chat functions.
				\item \textbf{Django Web Forum}: Built the form from scope through development and testing—user profile management page, comment creation page, thread creation page, topics page, friend request page, and upvote thread function. Implemented a search auto-complete using AJAX and jQuery. Created unit tests and executed testing and QA tasks.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Office Administrator}{True North Psychiatric Solutions}{August 2017 - January 2019}		
			\begin{itemize}
				\item Courses: Advanced Java III, Software Engineering, Mathematical Foundations of Computer Science I \& II.
				\item Promoted to Head TA in Fall 2004; led weekly meetings and supervised four other TAs.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Design Engineer, Intern}{Microsoft Corporation}{Summers 2001 -- 2003}
			Visual Studio Core (Summer 2003)		
			\begin{itemize}
				\item Implemented a user interface for the VS open file switcher (ctrl-tab) and extended it to tool windows.
				\item Created service to provide gradient across VS and VS add-ins. Optimized service via caching.
			\end{itemize}
			Programmer Productivity Research Center (Summers 2001, 2002)
			\begin{itemize}
				\item Built app to compute similarity of all methods in a code base; reduced time from $O(n^2)$ to $O(n\ log\ n)$. 
				\item Created test case generation tool which creates random XML docs from XML Schema.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Philadelphia, PA}{University of Pennsylvania}{Fall 2000 -- May 2005}
			\begin{itemize}
				\item M.S.E. in Computer and Information Science, May 2005. GPA: 3.6
				\item B.S.E. in Computer Science Engineering with Minor in Mathematics, May 2005.  In-major GPA: 3.4.
				\item Graduate Coursework: Software Foundations; Computer Architecture; Algorithms; Artificial Intelligence; Comparison of Learning Algorithms; Computational Theory.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship; Calculus III.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema 
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
